### 2022-05-30 main/chapter_2ljets.tex
add gmsb paragraph

The core idea behind the design of the $\twoljets$-electroweak analysis is to
update the regions of the partial Run~2 search in its $\twoljets$
channel~\cite{atlas_23l_SUSY_2016_24}.
A particular goal was to improve sensitivity by replacing their overlapping
`SR2-int' and `SR2-high' regions with orthogonal, combined selections.
\emph{I am grateful to Sarah Williams for suggesting this approach.}

As in the $\twoljets$-strong search, the partial Run~2 search chose one
$\twoljets$ signal region from an expected sensitivity for each signal point.
Two regions and the exclusion contours from that search are displayed in
Figure~\ref{fig:2ljets_23l_stuff}/

@@

\TODO{CMS papers, compare exclusion}

>>>>

The core idea behind the design of the $\twoljets$-electroweak analysis is to
update the regions of the partial Run~2 search in its $\twoljets$
channel~\cite{atlas_23l_SUSY_2016_24}, which also searched for signal models
producing chargino-neutralino pairs which decay via $W$ and $Z$ bosons.
A particular goal was to improve sensitivity by replacing their overlapping
`SR2-int' and `SR2-high' regions with orthogonal, combined selections.
\emph{I am grateful to Sarah Williams for suggesting this approach.}

As in the $\twoljets$-strong search, the partial Run~2 search chose one
$\twoljets$ signal region from an expected sensitivity for each signal point.
Two regions and the exclusion contours from that search are displayed in
Figure~\ref{fig:2ljets_23l_stuff}.

@@

Additionally, $\twoljets$ widens its scope to target a simplified GMSB model,
which has been illustrated in Figure~\ref{fig:2ljets_signal_diagrams}.
These two models behave similarly since both feature decays via massive bosons
($WZ$, $ZZ$ or $Zh$) to leptons and jets, in similarly structures decay trees
to pairs of invisible supersymmetric particles.
Although widening sensitivity to both models does sacrifice sensitivity to
either one, the increased degree of model independence is itself of value for
future reinterpretations of the data.

Searches by \cms\ have found comparable exclusions contours for the
C1N2 and GMSB models.
\TODO{CMS papers}
